%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Atsuko Tominaga} \\ \vspace{10pt}
    \small +43-677-64054156 $|$ \href{mailto:tominaga_atsuko@phd.ceu.edu}{\underline{tominaga\_atsuko@phd.ceu.edu}} $|$ 
    \href{https://atsukotominaga.com/}{\underline{atsukotominaga.com}} $|$
    \href{https://github.com/atsukotominaga}{\underline{github.com/atsukotominaga}} \\ \vspace{10pt}
    \small Last updated: \today
\end{center}

%-----------RESEARCH-----------
\section{Research Interests}

\small{My research interests are in the field of cultural transmission and social learning. I am investigating how learning from/with others has contributed to delivering cultural knowledge and skills to younger generations. I use an experimental method adapted from Cognitive Psychology and focus on the interaction between experts and novices in musical skill acquisition. I am currently working on how expert pianists modulate their performance to teach musical expressive techniques and how such modulations could be beneficial to novice learners.}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Central European University}{Austria}
      {PhD candidate in Cognitive Science}{Sep 2017 -- Present}
    \resumeSubheading
      {University of York}{United Kingdom}
      {Master of Research in Psychology}{Oct 2016 -- Jan 2018}
    \resumeSubheading
      {Kyoto University}{Japan}
      {Bachelor of Arts in Education (specialised in Psychology)}{Apr 2009 -- Mar 2013}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Academic Work Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {Technical Assistant, Coordinator}{ }
      {Kokoro Research Center, Kyoto University}{Apr 2016 -- Aug 2016}
      \resumeItemListStart
        \resumeItem{Ran experiments with Eyelink 1000 (SR Research)}
        \resumeItem{Organised research events for public}
        \resumeItem{Created necessary documents for research travel and funds}
      \resumeItemListEnd
    \resumeSubheading
      {Secretary of Director, Coordinator}{ }
      {Kokoro Research Center, Kyoto University}{Jun 2013 -- Jun 2014}
      \resumeItemListStart
        \resumeItem{Assisted international visiting researchers}
        \resumeItem{Organised research events and special undergraduate lectures}
        \resumeItem{Wrote summary reports of research events for lay audience}
        \resumeItem{Created necessary documents for research travel and funds}
      \resumeItemListEnd
    \resumeSubheading
      {Undergraduate Research Assistant}{ }
      {Kokoro Research Center, Kyoto University}{May 2011 -- Nov 2012}
      \resumeItemListStart
        \resumeItem{Ran experiments with Eyelink 1000 (SR Research)}
        \resumeItem{Created visual stimuli using Adobe Photoshop}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PUBLICATIONS-----------
\section{Publications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
        \item{
        {Scott-Phillips, T., \textbf{Tominaga, A.}, \& Miton, H. (in press). Ecological and psychological factors in the cultural evolution of music. \textit{Behavioral and Brain Sciences.} \\
       }}
        \item{
        {Ueda, Y., \textbf{Tominaga, A.}, Kajimura, S., \& Nomura, M. (2016). Spontaneous eye blinks during creative task correlate with divergent processing. \textit{Psychological research, 80}(4), 652-659.} \\
       }} 
 \end{itemize}

 %-----------PRESENTATIONS-----------
\section{Poster Presentations}
\begin{itemize}[leftmargin=0.15in, label={}]
   \small{\item{
    \textbf{Tominaga, A.}{, Sebanz, N., \& Knoblich, G. (2021). The Sound of Teaching Music: Experts’ sound modulation for novices. 11th Society for Tokyo Young Psychologists (STYP11), Japan.} \\
    \textbf{Tominaga, A.}{, Sebanz, N., \& Knoblich, G. (2019). The Sound of Teaching Music: Experts’ sound modulation for novices. 12th International Conference of Students of Systematic Musicology (SysMus19), Berlin, Germany.} \\
    \textbf{Tominaga, A.}{, Sebanz, N., \& Knoblich, G. (2019). The Sound of Teaching Music: Experts’ sound modulation for novices. 8th Joint Action Meeting (JAM8), Genoa, Italy.} \\
   }
   }
\end{itemize}

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Japanese (native), English (fluent)}, German \& Hungarian (elementary) \\
     \textbf{Programming}{: R, Python, Max MSP} \\
     \textbf{Extracurricular activities}{: CEU Student Union representative (2017-2019)}, Music Cognition Reading Group (2018-)
    }
    }
 \end{itemize}


%-------------------------------------------
\end{document}